% % Title and author(s)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{CS 703 Progress Report}
\author{Xiating Ouyang}
\date{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %
% % The next command allows your in import encapsulated
% % postscript files, .epsf or .eps files, which
% % contain vector graphic image data.
% %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
%\usepackage{charter,eulervm}

%\renewcommand{\baselinestretch}{1.5}

\usepackage{amsthm,amsmath,amssymb,upgreek,marvosym,mathtools}
\usepackage{array}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{paralist}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage{tabu}
\usepackage[nottoc]{tocbibind}
\usepackage[usenames,dvipsnames]{color}
\usepackage[pdftex,breaklinks,colorlinks,citecolor={blue}, linkcolor={blue},urlcolor=Maroon]{hyperref}
\usepackage{tkz-graph}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=25mm,
 top=20mm,
 right=25mm,
 }
\usetikzlibrary{automata, positioning,arrows,shapes,decorations.pathmorphing}

 \tikzset{
->, % makes the edges directed
>=stealth, % makes the arrow heads bold
node distance=3cm, % specifies the minimum distance between two nodes. Change if necessary.
every state/.style={thick, fill=gray!10}, % sets the properties for each ’state’ node
initial text=$ $, % sets the text that appears on the start arrow
}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{reduction}{Reduction}
\newtheorem{proposition}{Proposition}
\newtheorem{scolium}{Scolium}   %% And a not so common one.
\newtheorem{definition}{Definition}
%\newenvironment{proof}{{\sc Proof:}}{~\hfill QED}
\newenvironment{AMS}{}{}
\newenvironment{keywords}{}{}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\newcommand{\todo}{(TO BE CONTINUED...)}
\newcommand{\trans}[1]{
	#1^\mathsf{T}
}

\begin{document}
\newpage
\maketitle

\section{Project selection}
The term project is finally settled to be synthesis by examples with a focus on studying the expected size of the maximum clique in a graph following some random distributions. The ultimate goal is to find some probablistic graph models on which the synthesis by examples works practically. We will also conduct experiments on different graph models to evaluate their performance as in the number of consistent programs they missed and the expected search space size. 

\section{Current progress}
The current work involves reviewing existing literatures on graph models \cite{aiello2000random,easley2010networks} and the history of this problem \cite{gulwani2012spreadsheet,rolim2017learning,d2017nofaq}. The current focus is to implement the Power Law Graph generator in addition to the Erd\H{o}s-R\'enyi graph generator which has already been implemented.

The methods to compute maximal disjoint cliques and maximum clique are also implemented. The former so far is a trivial greedy algorithm while the latter employs enumeration. Note that finding the maximum clique in a graph is NP-complete, and hence this step is the bottleneck for the running time.

The undergoing proposal will comprise a detailed definition of the problem after the literature review, and specific deliverables will also be outlined. 
 
\bibliography{progress}{}
\bibliographystyle{plain}

\end{document}
